Condition-based Maintenance and Production Policies for Multi-Unit Systems

### 2018-06-20 report/paper_scm.tex
Rewrote introduction and appended system formulation

\title{Maintenance Policies for a Multi-Unit System with Adjustable Production Rates}
\author{Mark van der Broek}
\date{\today}

@@

\section{Introduction}	
% Good maintenance policies are required
Maintenance cost can constitute a large part of the total production costs. For example, \cite{GRABER2004861} states that maintenance costs can be at much as 30 percent of production costs for power plants, while \cite{BEVILACQUA200071} give an estimate of between 15 and 70 percent of the total production costs. For this reason, maintenance strategies have been extensively researched in the past decades. Reviews of past research have been published \citep{VANHORENBEEK2013499, OLDEKEIZER2017405}. Condition-based maintenance (CBM) is an advanced maintenance strategy that is based on performance and/or parameter monitoring and basing subsequent actions on the monitoring.

The coupling of production and maintenance for single-unit systems has been the subject of several studies in recent years. \cite{doi:10.1080/00207543.2013.843037} present an option-based cost model for scheduling a joint production and maintenance policy for a single-period, single-product system. \cite{doi:10.1080/00207543.2016.1174343}  study an integrated control strategy of production and maintenance for a machining system which produces a single type of product to meet the constant demand. The authors consider a single-unit system with a preventive maintenance policy.

Condition-based maintenance policies have been proposed for multi-unit systems with economic dependence \citep{OLDEKEIZER2016531}. \cite{OLDEKEIZER2018319} extend this research by including load sharing between units, that is, the deterioration of the functioning units is affected by the number of functioning units, where it is assumed that the load is shared uniformly over all functioning units. In this paper, we consider a system where we generalise this model and allow the load of all functioning units to depend on the current deterioration level of these units. Setting the load of the functioning units allows to cluster maintenance more effectively. In the rest of the paper, I will use the terminology production instead of load, however observe that production does not assumes the production of an item. As I will show in this paper, the effectiveness of setting the production (load) increases with the economic dependence between units.

@@

In this paper, I consider a joint production and maintenance strategy for a multi-unit system. I formulate the system as a Markov Decision Process and analyse the structural properties of the optimal policies. The model extends the model of \cite{OLDEKEIZER2018319} by allowing the production (load) to be set for all units. The deterioration process of the units is modelled by a discrete-time Markov chain with a known transition probability matrix. The production and maintenance strategy are jointly optimised, while in traditional methods the production is set be uniform for all functioning units.

@@

@@

The expected costs for a time unit by selecting maintenance action $r$ and in state $x$ is given by
$$
\bar{c}(x,r) = \begin{cases}
C + \sum_{i=1}^{n}c(x_i, r_i) &\text{if } r \text{ contains a maintenance action},\\
0 &\text{otherwise}.
\end{cases}
$$
In words, this means that if we do not perform maintenance on any unit for a given time period, we do not incur any costs. However, if we do perform maintenance, we incur the fixed cost $C$ and some corrective or preventive costs depending on the state of the maintained unit.
\subsection{Performance criteria}
As a performance criterion, we are interested in minimising the long-run average cost per time unit. In this way we can quantify the maintenance costs of a system over the life cycle, and identify the benefits of being able to set the production of each unit.

>>>>

\title{Condition-based Maintenance and Production Policies for Multi-Unit Systems}
\author{Mark van der Broek}
\date{\today}

@@

\section{Introduction}	
% Good maintenance policies are required
A large part of the total production costs is due to maintenance. \cite{GRABER2004861} states that maintenance costs can be at much as 30 percent of production costs for power plants, while \cite{BEVILACQUA200071} give an estimate of between 15 and 70 percent of the total production costs. \cite{wang2002survey} and \cite{ding2015maintenance} give a review of past research on maintenance policies. An increasingly popular maintenance strategy is condition-based maintenance (CBM), which uses conditioning information about components of a system to designs maintenance policies. Despite the increasing popularity of CBM, the implementation of CBM policies in practical applications is lagging behind \citep{keizer2017condition}. For this reason, research on CBM involves more complex systems with multiple dependent components \citep{}.

A general type of system is the $k$-out-of-$N$ system, which consists of $N$ components, and is functioning when at least $k$ components are functioning. \cite{OLDEKEIZER2018319} consider a $1$-out-of-$N$ system with economic dependence by imposing a fixed cost for performing maintenance and failure dependence by load sharing between units, that is, the deterioration of the functioning units is affected by the number of functioning units. The load of the functioning units is assumed to be shared uniformly over all functioning units.

In this paper, I consider a $k$-out-of-$N$ system with load sharing, which allows the load of all functioning units to depend on the current deterioration level of these units. Setting the load of the functioning units allows to cluster maintenance more effectively, due to greater control of the deterioration of the components of the total system. In the rest of the paper, I will use the terminology production instead of load, however observe that production does not assumes the production of an item. As I will show in this paper, the effectiveness of setting the production (load) increases with the economic dependence between units.

The coupling of production and maintenance for single-unit systems has been the subject of several studies in recent years. \cite{doi:10.1080/00207543.2013.843037} present an option-based cost model for scheduling a joint production and maintenance policy for a single-period, single-product system. \cite{doi:10.1080/00207543.2016.1174343} study an integrated control strategy of production and maintenance for a machining system which produces a single type of product to meet the deterministic demand. The authors consider a single-unit system with a preventive maintenance policy.

@@

In this paper, I consider a joint production and maintenance strategy for a multi-unit system. I formulate the system as a Markov Decision Process and analyse the structural properties of the optimal policies. The model extends the model of \cite{OLDEKEIZER2018319} by allowing the production (load) to be set for all units. The deterioration process of the units is modelled by a discrete-time Markov chain with a known transition probability matrix. The production and maintenance strategy are jointly optimised, while $k$-out-of-$N$ models usually assume that the production is shared uniformly over all functioning units.

@@

Since I assume that we can perform maintenance instantaneously, contrary to the work of \cite{OLDEKEIZER2018319}, I do impose a penalty if the system does not function, i.e., the number of functioning units is less than $k$. Instead, I restrict the set of feasible maintenance policies to be such that we need at least $k$ functioning units after the maintenance action.

@@

The expected costs for a time unit by selecting maintenance action $r$ and in state $x$ is given by
$$
\bar{c}(x,r) = \begin{cases}
C + \sum_{i=1}^{n}c(x_i, r_i) &\text{if } r \text{ contains a maintenance action},\\
0 &\text{otherwise}.
\end{cases}
$$
In words, this means that if we do not perform maintenance on any unit for a given time period, we do not incur any costs. However, if we do perform maintenance, we incur the fixed cost $C$ and some corrective or preventive costs depending on the state of the maintained unit.
\subsection{Performance criteria}
The performance criteria is to minimise the long-run average (maintenance) cost per time unit. This way, we can compare different condition-based maintenance and production strategies over the life cycle of the system.
